\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-06-20 TilingProjectDraft/tilingProject.tex
added entanglement plots in draft

>>>>

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{vne_kspace_all.pdf}
\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\) and \(k-\)space mutual information \(I_2(\vec k:-\vec k)\). The first two frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x\) direction as the transition parameter \(r\) is tuned through the metal-insulator transition, for two values of \(k_y\). The last two frames show the distribution of mutual information between two states \(\vec k\) and \(-\vec k\), in the \(k_x-k_y\) plane, for two values of \(r\). \(r/r_c=0.9\) represents a highly correlated metal, while \(r/r_c=1\) represents the non-Fermi liquid metal formed at the transition.}
\label{entanglement_kspace}
\end{figure}
